### 2016-03-10 paper/introduction.tex
yasu

\section{Introduction}
Parallel computation has changed the field of computing.  In the 90s,
most processors had single cores. In 2016, most processors have multiple
cores, often 4 or even 8. Cluster computing further expands the
potential of parallel computation, where one can easily launch a
processing job using hundreds or even thousands of computational nodes
in a cloud.
%
In the recent work on Go (AlphaGo from DeepMind), parallelization plays
a key role in the Monte-Carlo tree search~\cite{nature_alpha_go}.

Parallel computation offers tremendous potential for Computer Vision. As
image sensing technologies have gone through revolutions, we are in
ever growing demands in solving very large problems. One may need to
apply image denoising to 50 Megapixel images from latest digital
SLRs~\cite{canon?}, stitch thousands of images to generate gigapixel
panoramas~\cite{gigapan}, or solve volumetric reconstruction and
segmentation problems over a billion ($=1024^3$)
voxels~\cite{Joint3DSceneReconstructionandclassSegmentation}.
%
%
However, state-of-the-art algorithms are still inherently sequential in
many Computer Vision problems. Take a Fusion-Move algorithm
(FM)~\cite{viktor,second_order_stereo,else} for Markov Random Field
inference, for example. FM has been one of the most effective techniques
in solving the above
problems~\cite{fusion_moves_for_markov_random_field_optimization}.
%
It sequentially improves solution by fusing the current solution with a
solution proposal. Its successful applications range from optical flow,
stereo, image denoising, image inpainting, to image
segmentation~\cite{fusion_moves_for_markov_random_field_optimization}.

Unleashing the power of parallel computation in FM
% Breaking the sequential nature of FM
would then bring fundamental contributions to Computer
Vision. Currently, FM suffers from a few vital limitations due to its
sequential nature. First, standard FM allows only two options per
variable in each fusion, either the current solution or a
proposal~\cite{fusion_moves_for_markov_random_field_optimization}. Second,
only a single proposal generation scheme is used in each fusion
step.~\footnote{Recently, an extension of FM was proposed for layered
depthmap estimation~\cite{chen_2016}, where a solution subspace, instead
of a single solution, is proposed and fused with the current
solution. However, this approach is also limited to the use of one proposal
generation scheme in each fusion.}
%
Our approach, dubbed {\it Swarm Fusion} method (SF), makes a
few key distinctions from existing approaches: 1) Multiple threads (or
computing nodes) simultaneously keep and improve solutions; and 2) Each
fusion in each thread can take arbitrary number of proposals from
arbitrary combination of proposal generation schemes, even concurrent
solutions in the other threads, to be fused with the current solution.
%

We have evaluated our ideas on three problems in Computer Vision,
stereo, optical flow, and layered depthmap estimation. Our approach
outperforms all the other competing methods, especially for challenging
problems with a large label space.  Our approach is extremely simple in
concept, and is easily reproducible by standard Computer Vision engineers.
% will instantly benefit every Computer Vision researcher or
% engineer, who currently uses fusion move algorithm on multi-core
% environments to solve challenging problems.
% We will share our implementation of the algorithm.

>>>>

\section{Introduction}
Parallel computation has changed the field of computing.  In the 90s,
most processors had single cores. In 2016, most processors have multiple
cores, often 4 or even 8. Cluster computing further expands the
potential of parallel computation, where one can easily launch a
processing job using hundreds or even thousands of computational nodes
in a cloud.
%
In the recent work on the AI program playing the ancient Chinese board
game of {\it Go} (AlphaGo from DeepMind), parallelization plays a key
role in the Monte-Carlo tree search~\cite{nature_alpha_go}.

Parallel computation offers tremendous potential for Computer Vision. As
image sensing technologies have gone through revolutions, we are in
ever growing demands in solving very large problems. One may need to
apply image denoising to 50 Megapixel images from latest digital
SLRs~\cite{canon?}, stitch thousands of images to generate gigapixel
panoramas~\cite{gigapan}, or solve volumetric reconstruction and
segmentation problems over a billion ($=1024^3$)
voxels~\cite{Joint3DSceneReconstructionandclassSegmentation}.
%
%
However, state-of-the-art algorithms are still inherently sequential in
many Computer Vision problems. Take a Fusion Move method
(FM)~\cite{viktor,second_order_stereo,else}, which has been one of the
most effective techniques for the Markov Random Field (MRF) inference,
for example~\cite{fusion_moves}.
%
It sequentially improves solution by fusing the current solution with a
solution proposal. Its successful applications range from optical flow,
stereo, image denoising, image inpainting, to image
segmentation~\cite{fusion_moves_for_markov_random_field_optimization}.

Unleashing the power of parallel computation for effective MRF inference
% Breaking the sequential nature of FM
would then bring fundamental contributions to Computer
Vision. Currently, FM suffers from a few vital limitations due to its
sequential nature. First, standard FM allows only two options per
variable in each fusion, either the current solution or a
proposal~\cite{fusion_moves_for_markov_random_field_optimization}. Second,
only a single proposal generation scheme is used in each fusion
step.~\footnote{Recently, an extension of FM was proposed for layered
depthmap estimation~\cite{chen_2016}, where a solution subspace, instead
of a single solution, is proposed and fused with the current
solution. However, this approach is also limited to the use of one proposal
generation scheme in each fusion.}
%
Our approach, dubbed {\it Swarm Fusion} method (SF), makes a
few key distinctions from existing approaches: 1) Multiple threads (or
computing nodes) simultaneously keep and improve solutions; and 2) Each
fusion in each thread can take arbitrary number of proposals from
arbitrary combination of proposal generation schemes, even concurrent
solutions in the other threads, to be fused with the current solution.
%

We have evaluated the effectiveness of our approach over three problems
in Computer Vision, stereo, optical flow, and layered
depthmap estimation.
%
%Our approach outperforms all the other competing methods, especially for
%challenging problems with a large label space.
Our idea is very simple and the method is easily reproducible with
minimal coding.
% will instantly benefit every Computer Vision researcher or
% engineer, who currently uses fusion move algorithm on multi-core
% environments to solve challenging problems.
% We will share our implementation of the algorithm.
